### 2016-10-05 robust-software.tex
Reuse introduces dependencies

\item
Mention that reusing software introduces dependencies,
which can bring its own special pain.

@@

Unfortunately, the interface between two software packages can be a
source of considerable frustration. Support requests descend into
debugging errors produced by the other project.

>>>>

@@

Unfortunately, reusing software introduces dependencies, which can
bring their own special pain.  The interface between two software
packages can also be a source of considerable frustration: all too
often, support requests descend into debugging errors produced by the
other project.
